\documentclass[
    %a4paper, % Uncomment for A4 paper size (default is US letter)
    11pt, % Default font size, can use 10pt, 11pt, or 12pt
]{resume} % Use the resume class

\name{Maksim Lavrenko}

%\address{\href{https://github.com/maxinimus}{maxinimus (Github)}
%\href{https://www.linkedin.com/in/maksim-lavrenko/}{maksim-lavrenko (LinkedIn)}}

\address{\href{https://maxinimus.github.io}{Personal Website} \\ \href{https://github.com/maxinimus}{maxinimus (Github)} \href{https://www.linkedin.com/in/maksim-lavrenko/}{maksim-lavrenko (LinkedIn)}}

\address{(765) 767-1245 \\ maksim4lavrenko@gmail.com} % Contact information

\begin{document}
\small

\vspace*{-0.3cm}
\begin{rSection}{Education}
\vspace*{-0.3cm}
    \textbf{Purdue University} \\
    B.S. in Computer Science \& Mathematics \hfill GPA: 3.99/4.0 \quad August 2022 - May 2025 \\
    M.S. in Computer Science \hfill August 2024 - May 2026 \\
\end{rSection}
\vspace*{-0.3cm}
\begin{rSection}{Work Experience}
\vspace*{-0.2cm}
    \begin{rSubsection}{Teaching Assistant | CS 381 (current), CS 251 (current), CS 250, CS 182}{January 2024 - Present}{Purdue University, Department of Computer Science}{}
        \item Instructed and supported classes ranging from \textbf{60} to \textbf{800} students, adapting teaching strategies to varied class sizes.
        \item Conducted grading, held office hours, facilitated labs, and led collaborative sessions.
        \item Enhanced student comprehension and provided detailed feedback on assignments.
    \end{rSubsection}
    \vspace*{0,3cm}
    
\begin{rSubsection}{Community Assistant}{May 2024 - August 2024}{Purdue University, University Residences}{}
    \item Managed check-in and check-out procedures for over \textbf{100} attendees, ensuring a smooth transition.
    \item Handled emergency situations with priority, demonstrating capability in crisis management and quick decision-making.
    \item Provided high-level customer service, including the distribution and management of equipment, keys, and mail.
\end{rSubsection}

\end{rSection}


\vspace*{-0.3cm}
\begin{rSection}{Research Experience}
  \begin{rSubsection}{Ensemble Methods Survey}{August 2024 - December 2024}{Purdue University, Department of Computer Science}{}
  \item Conducted a \textbf{12 page} page survey of ensemble methods, including random forests, adaboost, and xgboost.
  \item Applied ensemble methods to \textbf{8} real-world datasets, including the \textbf{Adult dataset}, \textbf{bank marketing dataset}, and more.
  \item Used scikit-learn to implement models and evaluate their performance on various metrics.
  \end{rSubsection}
\end{rSection}

\begin{rSection}{Projects}
\vspace*{-0.3cm}
\begin{rSubsection}{}{}{\bf \href{}{Machine Learning Projects} $\mid$ Python, scikit-learn, TensorFlow }{\hfill \em August 2024 - Present}
    \item Developed a variety of machine learning models, such as kNN, linear regression, decision trees, and neural networks.
    \item Applied models to real-world datasets, such as the Iris dataset and the MNIST dataset.
    \item Utilized scikit-learn and TensorFlow to implement models and evaluate their performance.
\end{rSubsection}
%\begin{rSubsection}{}{}{\bf \href{https://github.com/maxinimus/MLEvsMAP}{MLE vs MAP Simulation Project} $\mid$ Python, NumPy, Matplotlib }{\hfill \em August 2024}
%    \item Developed a simulation to compare MLE and MAP methods in estimating the bias of a coin.
%    \item Demonstrated statistical model differences and efficiencies using Python, NumPy, and Matplotlib.
%    \item Created an interactive script for dynamic simulation parameter adjustments.
%\end{rSubsection}
\begin{rSubsection}{}{}{\bf \href{https://github.com/maxinimus/better-housing-bot}{Better Housing Bot} $\mid$ Python, Discord.py, BeautifulSoup }{\hfill \em December 2023}
    \item Created a \textbf{Discord bot} to streamline the search for on-campus housing at Purdue University.
    \item Implemented \textbf{real-time} dorm and apartment availability tracking through web scraping.
    \item Features included automatic updates, a notification mute function, and on-demand checks.
    \item Assisted \textbf{4} others in securing convenient on-campus housing, avoiding costlier alternatives.
\end{rSubsection}
\begin{rSubsection}{}{}{\bf \href{https://github.com/maxinimus/LaTeX-Matrix-Calculator}{LaTeX Matrix Calculator Website} $\mid$ Flask, numpy, React, Heroku }{ \hfill \em June - July 2023}
    \item Engineered a web application for LaTeX users to manage matrices and linear algebra operations.
    \item Provided LaTeX code generation for matrix operations, using Flask and React.
    \item Deployed on Heroku, optimizing for usability and access (currently inactive due to hosting costs).
\end{rSubsection}

\end{rSection}
\vspace*{-0.3cm}

\begin{rSection}{Coursework}
\vspace*{-0.3cm}
  \begin{tabular}{ @{} >{\bfseries}l p{14cm} }
    Computer Science & Advanced Algorithms, Data Structures, Machine Learning, Statistical Machine Learning, Artificial Intelligence, Theory of Computation, Computer Networks, Compilers  \\
    Mathematics & Linear Algebra 1 \& 2, Multivariable Calculus, Differential Equations, Probability Theory \\
  \end{tabular}
\end{rSection}
\vspace*{-0.2cm}

\vspace*{-0.3cm}
\begin{rSection}{Technical Strengths}
\vspace*{-0.3cm}


\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages & Python, C++, C, Java, R \\
    Machine Learning & TensorFlow, scikit-learn, PyTorch, Keras, pandas \\
    Web Technologies & Node.js, React.js, JavaScript, TypeScript, HTML5, CSS  \\
    Databases & SQL, PostgreSQL, MongoDB \\
    Other Tools & Git, LaTeX, Jupyter Notebook, Docker, Linux, Bash \\
\end{tabular} 


\end{rSection}

\end{document}


% Teaching Assistant for  CS 381, CS 251, CS 250, CS 182

% Purdue University
% West Lafayette

% Community Assistant

% Algorithms (CS 381), Data Structures (CS 251), Computer Architecture (CS 250), Discrete Mathematics (CS 182). Conducted grading, held office hours, facilitated labs, and led collaborative sessions. Enhanced student comprehension and provided detailed feedback on assignments.


% Managed check-in and check-out procedures for over 100 attendees, ensuring a smooth transition. Handled emergency situations with priority, demonstrating capability in crisis management and quick decision-making. Provided high-level customer service, including the distribution and management of equipment, keys, and mail.
